Response to Reviewers: Manuscript ID 17-1142.1: ``Learning Augmented Joint-Space Task-Oriented Dynamical Systems: A Linear Parameter Varying and Synergetic Control Approach"

### 2018-03-15 paper/reply_reviews/New_reply_to_comments_sina.tex
.

\textcolor{blue}{\texttt{Response:} \small This is not in general true. Based on the motion of the robot and its configuration, there might be cases where the motion generated by SEDS does not even reach the target. To clarify this, we have systematically studied the performance of the motion generated by JT-DS and SEDS+IK in terms of (i) reaching to the desired target and (ii) following the demonstrated end-effector motions, See Figure \ref{fig:SEDSvsJTDS}. We used the data-sets from the seven tasks mentioned in Section V.A to construct SEDS and JT-DS. Both methods are tested by the same the target and the initial configurations, which are extracted from demonstrations. We define $ x^*=[x^*_{ori};x^*_{pos}] $ as the target configuration that includes the desired position as well as the desired  orientation of the end-effector. The motion generated by SEDS is converted into the 7-DOF joints state using the damped least square IK solver.\\ 
In Figure \ref{fig:SEDSvsJTDSP:E} and Figure \ref{fig:SEDSvsJTDSO:E}, the error between the final location of the robot and the target is illustrated. As it can be seen, the motion generated by the proposed dynamical system reaches the target, whereas, the motion generated by SEDS does not, even though both models are theoretically stable. The main cause of failure for SEDS is due to the IK solver. As SEDS generates the motion of the robot without considering its joints configurations, the robot might reach its joint limits.  Whereas, as JT-Ds directly shapes the joints' motion, by learning the desired joint-space behavior, one can avoid these situations.   \\ 

@@

	\caption{Performance comparison between SEDS+IK and JT-DS while the initial and the target points are same. The error between the orientations is the difference between the first two columns of the corresponding rotation matrix representation.}

@@

In Figure \ref{fig:SEDSvsJTDSP} and Figure \ref{fig:SEDSvsJTDSO}, the error between the demonstrated and the excused motions are illustrated. As it can be seen, although JT-DS is not tailored for following the end-effector motions, its performance is mostly better than SEDS.\\
Although including this study would highlight one of the advantages of using JT-Ds over Cartesian-motion-generators, as this not the main focus of this paper and due to the space limitations, we have decided to not include this in the paper.}

>>>>

\textcolor{blue}{\texttt{Response:} \small This is, in general, not true. Based on the robot's motion and its configuration, there might be cases where the motion generated by SEDS does not even reach the target. To clarify this, we have systematically studied the performance of the motion generated by JT-DS and SEDS+IK in terms of (i) reaching to the desired target and (ii) following the demonstrated end-effector motions, See Figure \ref{fig:SEDSvsJTDS}. We used the data-sets from the seven tasks mentioned in Section V.A to construct SEDS and JT-DS. Both methods are tested by the same the target and the initial configurations, which were extracted from the demonstrations. We define $ x^*=[x^*_{ori};x^*_{pos}] $ as the target configuration that includes the desired position as well as the desired  orientation of the end-effector. The motion generated by SEDS is converted into the 7-DOF joints state using the damped least square IK solver.\\ 
In Figure \ref{fig:SEDSvsJTDSP:E} and Figure \ref{fig:SEDSvsJTDSO:E}, the error between the final location of the robot and the target is illustrated. As it can be seen, the motion generated by the proposed dynamical system reaches the target, whereas, the motion generated by SEDS does not; regardless of the fact that both models are theoretically stable. The main cause of failure for SEDS is due to the IK solver. As SEDS generates the motion of the robot without considering its joint configurations, the robot might reach its joint limits.  Whereas, as JT-Ds directly shapes the joints' motion, by learning the desired joint-space behavior, one can avoid these situations.   \\ 

@@

	\caption{The performance comparison between SEDS+IK and JT-DS while the initial and the target points are same. The error between the orientations is the difference between the first two columns of the corresponding rotation matrix representation.}

@@

In Figure \ref{fig:SEDSvsJTDSP} and Figure \ref{fig:SEDSvsJTDSO}, the error between the demonstrated and the excused motions are illustrated. As it can be seen, even though JT-DS is not tailored for following the end-effector motions, its performance is comparably better than SEDS.\\
Although including this study would highlight one of the advantages of using JT-DS over Cartesian-motion-generators, as this does not highlight the main focus of this paper and due to the space limitations, we have decided to not include this in the paper.}
